More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-04-23 2016-Weak-FH-Bisim/WeakBisim.tex
weak OT page 14

%%\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:

 \smallskip\noindent
 $  OT_2  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
   %                           \xrightarrow{in(?m,?b)}_{M1}
      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb];  Post=\{m_1\_m:=m, m_1\_b:=b\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\tau} \ostate{s_2,m_1,m_0,r_0}}
    $

@@

    \smallskip
At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
a subnet. One of its possible transition (synchronizing the hole $P$
with the $Protocol$) is:

    \smallskip
    The global states here have the same structure than
    in $OT\_2$, as the holes have no states. The assignment
    $Post$ uses a variable from the action of hole $P$ to set the
    value of the sender state variable $s1\_m$.
\end{example}

@@

The ``saturation'' step in the construction of the weak relation will
pick all $\tau^*$ and $\tau^*;a;\tau^*$ sequences from the OA, and build a weak
OT from each sequence. Here is one example:

\noindent
$\ostate{1000}\OTarrow{m\_rec(m,x), \phi_1 = [x=s_1\_b \land
    m=s_1\_m]}\ostate{2100}$\\
and $\qquad\ostate{2100}$ variable assignments are: $\psi_1 = \{m_1\_m:=m; m_1\_x:=x; s_2\_b:=s_1\_b\}$;\\
\\
$\ostate{2100}\OTarrow{\tau <m\_send(m_1\_m,m_1\_x), r\_rec(?m',?b)>,
  \phi_2 = [r_0\_b=b \land m'=m_1\_m \land b=m_1\_x]}\ostate{2001}$\\
and $\qquad\ostate{2001}$ assignments: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
; s_2\_b:=s_1\_b\}$;\\
\\
$\ostate{2001}\OTarrow{v,
  \phi_3 = [v=out(r_1\_m)]}\ostate{2002}$\\
and $\qquad\ostate{2002}$ variablesassignments: $\psi_3 = \{r_2\_b:=r_1\_b; s_2\_b:=s_1\_b\}$;\\

@@

 \noindent
 $$\ostate{1000}\OTWeakarrow{v,
   [v=out(s_1\_m)\land r_0\_b=s_1\_b],\{r_2\_b:=r_0\_b\}} \ostate{2002}$$
%% \\
%% $\phi=[x=s_1\_b \land m=s_1\_m\\
%%   \land r_0\_b=b \land m'=m_1\_m \land b=m_1\_x\\
%%   \land v=out(r_1\_m)]\\
%% and \\
%% \psi= \{r_2\_b:=r_0\_b\}$

>>>>

%%\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
a subnet. One of its possible transition (synchronizing the hole $P$
with the $Protocol$) is:

    \smallskip
    The global states here have the same structure than
    in $OT\_2$, as the holes have no states. The assignment
    $Post$ uses a variable from the action of hole $P$ to set the
    value of the sender state variable $s1\_m$.

  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:

 \smallskip\noindent
 $  OT_2  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
   %                           \xrightarrow{in(?m,?b)}_{M1}
   \emptyset; Pred=[send(SV2\_m, SV2\_b)=send(s_1\_m, s_1\_sb);in(SV2\_m, SV2\_b)=in(?m,?b)];  \\ Post=\{m_1\_m:=?m, m_1\_b:=?b, s_2\_sb:=s_1\_sb\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(SV2\_m, SV2\_b)}} \ostate{s_2,m_1,m_0,r_0}}
    $

    \ERIC{Apres resolution de l'unification:}

     $  OT_2  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
   %                           \xrightarrow{in(?m,?b)}_{M1}
      \emptyset; Pred=[s_1\_m=SV2\_m, SV2\_m=?m, s_1\_sb=SV2\_b, SV2\_b=?b];  \\ Post=\{m_1\_m:=?m, m_1\_b:=?b, s_2\_sb:=s_1\_sb\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
    $

    \ERIC{Apres application des substitutions et simplification du predicat:}

     $  OT_2  = \openrule{
      \emptyset; Pred=true;  \\ Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
                      }
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
    $

@@

    \smallskip

@@

The ``saturation'' step in the construction of the weak relation will
pick all $\tau^*$ and $\tau^*;a;\tau^*$ sequences from the OA, and build a weak
OT from each sequence. Here is one example of a short sequence,
starting with the open transition $OT_2$ of page \pageref{OT:ABP},
then transmitting the message to the receiver (if the sender and
receiver control bits are equal), and to the environnement. The two
firts OTs are internal, the last one is visible, so it constitute a
$\tau;\tau;a$ weak transition.

\noindent
     $  \openrule{
      \emptyset; Pred=true; Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
                      }
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
    $

\medskip\noindent
     $  \openrule{
      \emptyset; Pred=[r_0\_rb=?b' \land ?m'=m_1\_m \land ?b=m_1\_b \land SV3\_m=?m' \land SV3\_b=?b'];
      \\ Post=\{r_1\_rb:=r_0\_rb; r_1\_m:=?m'; r_1\_b:=?b'      \}
                      }
    {\ostate{s_2,m_1,m_0,r_0} \OTarrow{\underline{recv(SV3\_m, SV3\_b)}} \ostate{s_2,m_0,m_0,r_1}}
    $

    \ERIC{Apres simplification:}
\medskip\noindent
     $  \openrule{
      \emptyset; Pred=[r_0\_rb=m_1\_b];
      \\ Post=\{r_1\_rb:=r_0\_rb; r_1\_m:=m_1\_m; r_1\_b:=m_1\_b      \}
                      }
    {\ostate{s_2,m_1,m_0,r_0} \OTarrow{\underline{recv(m_1\_m,m_1\_b)}} \ostate{s_2,m_0,m_0,r_1}}
    $
    \\

\medskip\noindent
     $  \openrule{
  \emptyset; Pred=true; Post=r_2\_b:=r_1\_b; s_2\_b:=s_1\_b   \}
                      }
    {\ostate{s_2,m_0,m_0,r_1} \OTarrow{out(r_1\_m)} \ostate{s_2,m_0,m_0,r_2}}
    $
    \\

    \bigskip
    \ERIC{Anciennes versions:}
$\ostate{1000}\OTarrow{\underline{send(m,b)}, \phi_1 = [x=s_1\_b \land
    m=s_1\_m]}\ostate{2100}$\\
and $\qquad\ostate{2100}$ variable assignments are: $\psi_1 = \{m_1\_m:=m; m_1\_x:=x; s_2\_b:=s_1\_b\}$;\\
\\
$\ostate{2100}\OTarrow{\tau <m\_send(m_1\_m,m_1\_x), r\_rec(?m',?b)>,
  \phi_2 = [r_0\_b=b \land m'=m_1\_m \land b=m_1\_x]}\ostate{2001}$\\
and $\qquad\ostate{2001}$ assignments: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
; s_2\_b:=s_1\_b\}$;\\
\\
$\ostate{2001}\OTarrow{v,
  \phi_3 = [v=out(r_1\_m)]}\ostate{2002}$\\
and $\qquad\ostate{2002}$ variablesassignments: $\psi_3 = \{r_2\_b:=r_1\_b; s_2\_b:=s_1\_b\}$;\\

@@

 \noindent
 $$ \openrule{
   \emptyset; Pred=[r_0\_b=s_1\_b]; Post= \{r_2\_b:=r_0\_b  \}
   }
   {\ostate{s_1,m_0,m_0,r_0}\OTWeakarrow{out(s_1\_m)} \ostate{s_2,m_0,m_0,r_2}}$$
%% \\
%% $\phi=[x=s_1\_b \land m=s_1\_m\\
%%   \land r_0\_b=b \land m'=m_1\_m \land b=m_1\_x\\
%%   \land v=out(r_1\_m)]\\
%% and \\
%% \psi= \{r_2\_b:=r_0\_b\}$
